Modelling spatial structure in small-area estimation

### 2022-07-31 src/docs_paper/paper.Rmd
Upload manuscript

<!-- \begin{figure} -->
<!-- \centering -->
<!-- \includegraphics[width=\textwidth]{depends/integration-method.pdf} -->
<!-- \caption{Three ways to choose integration points with $L_i = 10$ for all $i$ in Malawi, as implemented by \texttt{sf::st\_sample} [@pebesma2018sf].} -->
<!-- \label{fig:41} -->
<!-- \end{figure} -->

@@

We compared model performance as, again varying the spatial random effect specification, in estimating HIV prevalence in adults aged $15-49$ across four countries in sub-Saharan Africa: Côte d'Ivoire ($n = 33$), Malawi ($n = 28$), Tanzania ($n = 159$) and Zimbabwe ($n = 60$).
As with the simulation study, \textsf{R} code for this study is available from \url{https://github.com/athowes/areal-comparison}.

>>>>

\begin{figure}
\centering
\includegraphics[width=\textwidth]{depends/integration-method.pdf}
\caption{Three ways to choose integration points with $L_i = 10$ for all $i$ in Malawi, as implemented by \texttt{sf::st\_sample} [@pebesma2018sf].}
\label{fig:41}
\end{figure}

@@

We compared model performance in estimating HIV prevalence in adults aged $15-49$ across four countries in sub-Saharan Africa: Côte d'Ivoire ($n = 33$), Malawi ($n = 28$), Tanzania ($n = 159$) and Zimbabwe ($n = 60$), again varying the spatial random effect specification.
As with the simulation study, \textsf{R} code for this study is available from \url{https://github.com/athowes/areal-comparison}.
